exponential Bradley-Terry

### 2025-11-27 inst/exponential_BT.Rmd
note on time to process
analysis of skating

@@

>>>>

<font size="1">
(takes maybe two or three hours to run without cache; each
<tt>parkrunlikefunobs</tt> chunk takes maybe thirty minutes).
</font>

@@

# Skating

```{r, startskating, cache=TRUE}
sk <- skating
pnames(sk) <- names(sort(skating_maxp, decreasing=TRUE))
maxp(sk)
```

```{r moreskating, cache=TRUE}
skater_strengths <- function(x){
    p <- BT(23, x)
    names(p) <- pnames(sk)
    return(p)
}
skater_strengths(0.5)
```

```{r doskating, cache=TRUE}
gvec <- seq(from=0.5, by=0.01, to=0.65)
f <- function(g){loglik(skater_strengths(g), sk)}
L <- sapply(gvec, f)
L <- L-max(L)
```

```{r}
plot(gvec,L,type="b")
abline(h = c(0,-2))
grid()
```

```{r testskating, cache=TRUE}
skater_strengths(0.57)
skating_test <- knownp.test(sk, skater_strengths(0.57))
skating_test
```

```{r}
xn <- skating_test$null_estimate
xa <- skating_test$alternative_estimate
xn <- log10(xn)
xa <- log10(xa)
par(pty="s")
plot(xn,xa,xlim=c(-6,0),ylim=c(-6,0))
abline(0,1)
```
